Output Summary

### 2021-08-05 03-post-process/output-plots.Rmd
Add plots that show the multinomial sample sizes for weir and carcass composition sampling

@@

@@

@@

@@

plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^phi_Sb_Sa[.+,pop]", pop = j)), with(jags_data, carcs_spawned[,j]/carcs_sampled[,j])[observable], main = pops[j], ylim = c(0,1))
  par(mar = c(1.5,1.5,2,0.5), yaxs = "i")

>>>>

# for multinomial sample size
weir_sample_size = function(j) {
  par(mar = c(3,3,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
  mp = barplot(jags_data$weir_nx_obs[observable,j], xaxt = "n", col = alpha("skyblue2", 0.5), border = "blue",
               ylim = c(0, max(jags_data$weir_nx_obs[observable,j], na.rm = TRUE)),
               xlab = "Return Year", ylab = "Adults at Weir Sampled for Composition")
  usr = par("usr")
  at_x = seq(1, length(observable), 4)
  axis(side = 1, at = mp[at_x], labels = substr(names(jags_data$weir_nx_obs[observable,j]), 3, 4)[at_x])
  segments(usr[1], usr[3], usr[2], usr[3], xpd = TRUE)
}

@@

#### Total Sample Size {.tabset .tabset-pills}

These figures show the number of samples gathered for age/sex/origin composition information during carcass surveys. The model will fit more closely to years with more samples.

```{r cat-weir-ss, fig.width = 6, fig.height = 4}
weir_sample_size(j_cat)
```

```{r los-weir-ss, fig.width = 6, fig.height = 4}
weir_sample_size(j_los)
```

```{r min-weir-ss, fig.width = 6, fig.height = 4}
weir_sample_size(j_min)
```

```{r ugr-weir-ss, fig.width = 6, fig.height = 4}
weir_sample_size(j_ugr)
```

@@

# for multinomial sample size
carc_sample_size = function(j) {
  par(mar = c(3,3,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
  mp = barplot(jags_data$carc_nx_obs[observable,j], xaxt = "n", col = alpha("skyblue2", 0.5), border = "blue",
               ylim = c(0, max(jags_data$carc_nx_obs[observable,j], na.rm = TRUE)),
               xlab = "Return Year", ylab = "Carcasses Sampled for Composition")
  usr = par("usr")
  at_x = seq(1, length(observable), 4)
  axis(side = 1, at = mp[at_x], labels = substr(names(jags_data$carc_nx_obs[observable,j]), 3, 4)[at_x])
  segments(usr[1], usr[3], usr[2], usr[3], xpd = TRUE)
}

@@

#### Total Sample Size {.tabset .tabset-pills}

These figures show the number of samples gathered for age/sex/origin composition information during carcass surveys. The model will fit more closely to years with more samples.

```{r cat-carc-ss, fig.width = 6, fig.height = 4}
carc_sample_size(j_cat)
```

```{r los-carc-ss, fig.width = 6, fig.height = 4}
carc_sample_size(j_los)
```

```{r min-carc-ss, fig.width = 6, fig.height = 4}
carc_sample_size(j_min)
```

```{r ugr-carc-ss, fig.width = 6, fig.height = 4}
carc_sample_size(j_ugr)
```

@@

plot_f = function(j) {
  par(yaxs = "r")
  plot_tseries(post_summ(post, sub_index("^phi_Sb_Sa[.+,pop]", pop = j)), with(jags_data, carcs_spawned[,j]/carcs_sampled[,j])[observable], main = pops[j], ylim = c(0,1))
  par(mar = c(1.5,1.5,2,0.5), yaxs = "i")
